---
output: github_document
---
[![Build Status](https://travis-ci.org/oganm/geneSynonym.svg?branch=master)](https://travis-ci.org/oganm/geneSynonym) [![codecov](https://codecov.io/gh/oganm/geneSynonym/branch/master/graph/badge.svg)](https://codecov.io/gh/oganm/geneSynonym)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
devtools::load_all()
```
# Gene Synonym
An r package that works as a wrapper to synonym information in ftp://ftp.ncbi.nlm.nih.gov/gene/DATA/gene_info.gz. Updates weekly since 8th of Match 2017

Available species are

```{r}
geneSynonym::taxData
```

More species can be added on request


Installation
============
```r
library(devtools)
install_github('oganm/geneSynonym')
```

Usage
===========
The output is a nested list since gene synonyms are not nececarilly unique. For instance

```{r}
mouseSyno('Tex40')
```

Names of vectors within the list are NCBI ids.

Input is a vector of gene names/NCBI ids and a tax identifier. Alternatively shorthand functions exist for human and mouse.

```{r}
geneSynonym(c('Eno2','Mog'), tax = 10090)

geneSynonym(c('Eno2','Mog'), tax = 10090)

mouseSyno(c('Eno2',17441))

humanSyno('MOG')
```
